Mining HIV Trends in Social Media Data

### 2016-04-13 draft/draft.tex
fix git ignore

@@

@@

\begin{figure}
\centering
\includegraphics[height=2.5in, width=3.5in]{map}
\caption{Plot of geolocated tweets.}
\end{figure}

@@

@@

% table 1
\begin{table}
\centering
\caption{Cosine Similarity to 'truvada'}
\begin{tabular}{|l|c|} \hline
Related Word & Cosine Similarity to 'truvada'\\ \hline
prep & 0.836507\\ \hline
charliesheen & 0.774535\\ \hline
worldaidsday & 0.759242\\ \hline
hivtestweek & 0.797361\\ \hline
hiv & 0.744817\\ \hline
hivaids & 0.730966\\ \hline
aidsfreefuture & 0.721897\\ \hline
icasa2015 & 0.713624\\ \hline
benegative & 0.709129\\ \hline
martinshkreli & 0.702565\\ \hline
\hline\end{tabular}
\end{table}

% table 2
\begin{table}
\centering
\caption{Cosine Similarity to '\#truvada'}
\begin{tabular}{|l|c|} \hline
Related Hashtag/Tweet & Cosine Similarity to '\#truvada'\\ \hline
\#prep & 0.740855\\ \hline
\#hiv & 0.646245\\ \hline
685501883448963072 & 0.582529\\ \hline
\#prevention & 0.0.578786\\ \hline
\#potus & 0.561461\\ \hline
688733331081527296 & 0.558048\\ \hline
\#[Japanese "email friend"] & 0.557464\\ \hline
\#[Japanese "sex friend"] & 0.556990\\ \hline
\#bbbh & 0.547450\\ \hline
\#cure & 	0.545497\\ \hline
\hline\end{tabular}
\end{table}

@@

@@

@@

% table 3
\begin{table*}
\centering
\caption{Topics Present in 500 HIV/PrEP related Timelines}
\begin{tabular}{|l|c|c|c|c|c|} \hline
Topic ID & Word1 & Word2 & Word3 & Word4 & Word5\\ \hline
0 & 0.002*que & 0.001*por & 0.001*para & 0.001*milan & 0.001*een\\ \hline
1 & 0.001*yg & 0.001*ini & 0.001*yang & 0.000*aku & 0.000*breakingbad\\ \hline
2 & 0.001*lmao & 0.001*nigeria & 0.000*syria & 0.000*nigga & 0.000*kca\\ \hline
3 & 0.000*ntv & 0.000*inspiringthinkn & 0.000*ktnkenya & 0.000*haber & 0.000*tuscany\\ \hline
4 & 0.003*gurmeetramrahim & 0.001*ang & 0.001*ng & 0.001*ji & 0.001*ako\\ \hline
5 & 0.001*remedies & 0.000*tw & 0.000*mx & 0.000*rid & 0.000*momlife\\ \hline
6 & 0.000*flipboard & 0.000*mongolia & 0.000*gettingtozero & 0.000*blackburn & 0.000*occupy\\ \hline
7 & 0.002*newsbreakslive & 0.002*drudgereport & 0.000*woof & 0.000*und & 0.000*der\\ \hline
8 & 0.001*giveaway & 0.001*xx & 0.001*photography & 0.001*startups & 0.001*anc\\ \hline
9 & 0.001*realdonaldtrump & 0.001*lgbt & 0.001*hiring & 0.001*uniteblue & 0.001*tedcruz\\ \hline
\hline\end{tabular}
\end{table*}

@@

@@

The sentiment results aren't perfect, but they do help us identify positive individials in PrEP and HIV public health such as user @greg0wen. The sentiment tweets also let us uncover some of the prevailing stigmas and negative sentiments surrounding PrEP usage.

>>>>

 - social impact issues, efficacy, adherence issues, other STDs, Austin (Scott County) Indiana Outbreak as example

 - specifically other papers that did mining Twitter for HIV

@@

 - theory and application examples

@@

\begin{figure}
\centering
\includegraphics[height=2.5in, width=3.5in]{map.pdf}
\caption{Plot of geolocated tweets.}
\end{figure}

@@

% show text of relevent tweets from d2v

% talk a bit about pre processing

@@

% table 1 - w2v truvada
\begin{table}
\centering
\caption{Cosine Similarity to 'truvada'}
\begin{tabular}{|l|c|} \hline
Related Word & Cosine Similarity to 'truvada'\\ \hline
prep & 0.836507\\ \hline
charliesheen & 0.774535\\ \hline
worldaidsday & 0.759242\\ \hline
hivtestweek & 0.797361\\ \hline
hiv & 0.744817\\ \hline
hivaids & 0.730966\\ \hline
aidsfreefuture & 0.721897\\ \hline
icasa2015 & 0.713624\\ \hline
benegative & 0.709129\\ \hline
martinshkreli & 0.702565\\ \hline
\hline\end{tabular}
\end{table}

% table 2 - d2v PrEP
\begin{table}
\centering
\caption{Cosine Similarity to '\#truvada'}
\begin{tabular}{|l|c|} \hline
Related Hashtag/Tweet & Cosine Similarity to '\#truvada'\\ \hline
\#prep & 0.740855\\ \hline
\#hiv & 0.646245\\ \hline
685501883448963072 & 0.582529\\ \hline
\#prevention & 0.0.578786\\ \hline
\#potus & 0.561461\\ \hline
688733331081527296 & 0.558048\\ \hline
\#[Japanese "email friend"] & 0.557464\\ \hline
\#[Japanese "sex friend"] & 0.556990\\ \hline
\#bbbh & 0.547450\\ \hline
\#cure & 	0.545497\\ \hline
\hline\end{tabular}
\end{table}

% show PCA for each table above (remember to mention percent varience)

@@

% PrEP related trends (2 topic time series worth)
% World AIDs day as validation (1 topic time series)

@@

% this will take time to complete

@@

% table 3 - top topics
\begin{table*}
\centering
\caption{Topics Present in 500 HIV/PrEP related Timelines}
\begin{tabular}{|l|c|c|c|c|c|} \hline
Topic ID & Word1 & Word2 & Word3 & Word4 & Word5\\ \hline
0 & 0.002*que & 0.001*por & 0.001*para & 0.001*milan & 0.001*een\\ \hline
1 & 0.001*yg & 0.001*ini & 0.001*yang & 0.000*aku & 0.000*breakingbad\\ \hline
2 & 0.001*lmao & 0.001*nigeria & 0.000*syria & 0.000*nigga & 0.000*kca\\ \hline
3 & 0.000*ntv & 0.000*inspiringthinkn & 0.000*ktnkenya & 0.000*haber & 0.000*tuscany\\ \hline
4 & 0.003*gurmeetramrahim & 0.001*ang & 0.001*ng & 0.001*ji & 0.001*ako\\ \hline
5 & 0.001*remedies & 0.000*tw & 0.000*mx & 0.000*rid & 0.000*momlife\\ \hline
6 & 0.000*flipboard & 0.000*mongolia & 0.000*gettingtozero & 0.000*blackburn & 0.000*occupy\\ \hline
7 & 0.002*newsbreakslive & 0.002*drudgereport & 0.000*woof & 0.000*und & 0.000*der\\ \hline
8 & 0.001*giveaway & 0.001*xx & 0.001*photography & 0.001*startups & 0.001*anc\\ \hline
9 & 0.001*realdonaldtrump & 0.001*lgbt & 0.001*hiring & 0.001*uniteblue & 0.001*tedcruz\\ \hline
\hline\end{tabular}
\end{table*}

@@

% top positive and negative example tweets
% report accuracy
% (potentially) report topic modeling on top postive and negative PrEP tweets

@@

The sentiment results aren't perfect, but they do help us identify positive individuals in PrEP and HIV public health such as user @greg0wen. The sentiment tweets also let us uncover some of the prevailing stigmas and negative sentiments surrounding PrEP usage.
